Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-16 manuscript.Rmd
Minor edit

@Hyde2008 report that effect sizes for gender differences in mathematics tests across the 7 million students in the US represent trivial differences, which the authors specify as effect sizes smaller than $d = `r printnum(sesoi)`$. For example, in grade 3 the difference is $d = 0.04$, with a standard error of 0.002. When we perform equivalence tests on the meta-analytic effect sizes of IQ difference for grades 2 to 11 (using an alpha level of `r printp(alpha)` to correct for multiple comparisons), using equivalence bounds of $\Delta_{L} = -0.1$ and $\Delta_{U} = 0.1$, we see that indeed, all effect size estimates are measured with such high precision that they are statistically equivalent and can be considered trivially small, according to the authors’ definition (Figure 2C). In the case of grade 3, $z = `r printnum(max(gr3$TOST_Z1, gr3$TOST_Z2))`$, $p = `r printnum(max(gr3$TOST_p1, gr3$TOST_p2))`$ However, note that all of the effects are also statistically different from zero, as one might expect when there is no random assignment to conditions and samples sizes are very large. For grade 3, $z = `r printnum(gr3.z)`$, $p = `r printnum(gr3.p)`$. This is one way in which the use of equivalence tests improves hypothesis testing procedures in science, by allowing researchers to distinguish between statistical significance and practical significance.

>>>>

@Hyde2008 report that effect sizes for gender differences in mathematics tests across the 7 million students in the US represent trivial differences, which the authors specify as effect sizes smaller than $d = `r printnum(sesoi)`$. For example, in grade 3 the difference is $d = 0.04$, with a standard error of 0.002. When we perform equivalence tests on the meta-analytic effect sizes of IQ difference for grades 2 to 11 (using an alpha level of `r printp(alpha)` to correct for multiple comparisons), using equivalence bounds of $\Delta_{L} = -0.1$ and $\Delta_{U} = 0.1$, we see that indeed, all effect size estimates are measured with such high precision that they are statistically equivalent and can be considered trivially small, according to the authors’ definition (Figure 2C). In the case of grade 3, $z = `r printnum(max(gr3$TOST_Z1, gr3$TOST_Z2))`$, $p = `r printnum(max(gr3$TOST_p1, gr3$TOST_p2))`$. However, note that all of the effects are also statistically different from zero, as one might expect when there is no random assignment to conditions and samples sizes are very large. For grade 3, $z = `r printnum(gr3.z)`$, $p = `r printnum(gr3.p)`$. This is one way in which the use of equivalence tests improves hypothesis testing procedures in science, by allowing researchers to distinguish between statistical significance and practical significance.
